The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-11 article.tex
Removed a comma

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\parttitle{Background}
The Chemistry Development Kit (CDK) is a 
widely used open source cheminformatics toolkit, providing data
structures to represent chemical concepts along with methods to
manipulate such structures and perform computations on them. The
library implements a wide variety of cheminformatics algorithms
ranging from chemical structure canonicalization to molecular
descriptor calculations and pharmacophore perception. Over the
last ten years, the code base has grown significantly resulting in
many, complex interdependencies among components and poor
performance of many algorithms. 
\parttitle{Results}
We report improvements to the CDK since the 1.2 release series,
specifically addressing the increased functional complexity and poor
performance. We first summarize the addition of new, and
improvements to existing functionality that has led to significant
improvement in performance and support for important chemistry
features including atom type perception, substructure searching, molecular
fingerprints, rendering of molecules, and handling of molecular formulas.
Second, we outline how the CDK has evolved with respect to
quality control and the approaches we have adopted to ensure stability, including
a code review mechanism.
\parttitle{Conclusions}
This paper highlights the our continued efforts to provide a community
driven, open source
cheminformatics library, and show that such collaborative projects can exist over
extended periods of time, resulting in a high-quality and performant
library. By taking 
advantage of community support and contributions, we show 
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computing software.
\end{abstract}

>>>>

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\parttitle{Background}
The Chemistry Development Kit (CDK) is a 
widely used open source cheminformatics toolkit, providing data
structures to represent chemical concepts along with methods to
manipulate such structures and perform computations on them. The
library implements a wide variety of cheminformatics algorithms
ranging from chemical structure canonicalization to molecular
descriptor calculations and pharmacophore perception. Over the
last ten years, the code base has grown significantly resulting in
many complex interdependencies among components and poor
performance of many algorithms. 
\parttitle{Results}
We report improvements to the CDK since the 1.2 release series,
specifically addressing the increased functional complexity and poor
performance. We first summarize the addition of new, and
improvements to existing functionality that has led to significant
improvement in performance and support for important chemistry
features including atom type perception, substructure searching, molecular
fingerprints, rendering of molecules, and handling of molecular formulas.
Second, we outline how the CDK has evolved with respect to
quality control and the approaches we have adopted to ensure stability, including
a code review mechanism.
\parttitle{Conclusions}
This paper highlights the our continued efforts to provide a community
driven, open source
cheminformatics library, and show that such collaborative projects can exist over
extended periods of time, resulting in a high-quality and performant
library. By taking 
advantage of community support and contributions, we show 
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computing software.
\end{abstract}
